---
title: "R Programming and Tidyverse"
author: "Muhammad Aziz Muslim"
date: "2023-05-21"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bulleted List
- Item 1
  - Sub-item A
  - Sub-item B
- Item 2
- Item 3

# Numbered List
1. First item
2. Second item
3. Third item

# Italics and Bold
Some *italicized* words and **bold** words.

## Header Level 2

### Header Level 3

# Results without code
```{r, echo=FALSE}
results <- 2 + 2
results

```

# Creating Table with 3 columns 3 rows using characters
```{r echo=FALSE, results='asis'}
library(knitr)
table.data <- data.frame(City = c("Tokyo", "Vienna", "Beijing"), 
                         Country = c("Japan", "Austria", "China"), 
                         Continent = c("Asia", "Europe", "Asia"))
kable(table.data, caption = "Top three beautiful city")
```

# Creating plot with code included
```{r}
plot(x = 1:5, y = 1:5)
```
# Session Info
```{r}
sessionInfo()
```

# Execution of Rmarkdwon file
rmarkdown::render("MuhammadAzizMuslim_Week1_Rprogramming.Rmd")
